---
title: "Tox Notebook"
always_allow_html: true
output:
  html_document: default
  pdf_document: default
---

# Introduction 

This notebook reports toxicology features of interest from CompTox and ICE.

# Endpoints of interest

The endpoints of interest used in this notebook include but are not limited to:
- Acute Toxicity: Eye Irritation, Skin Irritation, Skin Sensitization, Repeat Dose Toxicity, Developmental Reproductive Toxicity, Carcinogenicity, Genotoxicity, Toxicokinetics, Metabolism, Dermal Penetration, Inhalation, Neurotoxicity, Type 1 allergy, Photo allergy, Photo sensitization, Phototoxicity

# Load required libraries
```{r, message=FALSE}
library(DT)
library(arrow)
library(dplyr)
library(tidyr)
```

# Toxicity

## Eye Irritation
```{r, message=FALSE}
eye_irritation <- read_parquet("../../ICE/data/Eye_Irritation.parquet") |> 
  select("Chemical Name", "Endpoint")
datatable(eye_irritation[1:100, ])
```

## Inhalation Toxicity 
```{r, message=FALSE}
inhalation_toxicity <- read_parquet("../../ICE/data/Acute_Inhalation_Toxicity.parquet") |> 
  select("Product Name", "Active Ingredient", "Test Organism", 
         "Clinical Observations", "Gross Pathology")
datatable(inhalation_toxicity[1:100, ])
```

## Skin
### Dermal Toxicity
```{r, message=FALSE}
dermal_toxicity <- read_parquet("../../ICE/data/Acute_Dermal_Toxicity.parquet") |> 
  select("Product Name", "Active Ingredient", "Test Organism", 
         "Dose (mg/kg)", "Clinical Observations", "Gross Pathology")
datatable(dermal_toxicity[1:100, ])
```

### Skin Sensitization
```{r, message=FALSE}
skin_sensitization <- read_parquet("../../ICE/data/Skin_Sensitization.parquet") |> 
  select("Chemical Name", "Endpoint",
  "Species", "tissue", "lesion", "location", 
  "gene", "pubmedid")
datatable(skin_sensitization[1:100, ])
```

## Carcinogenic 
```{r, message=FALSE}
Cancer <- read_parquet("../../ICE/data/Cancer.parquet") |> 
  select("Formulation Name", "Chemical Name", "Species", 
         "Level of evidence", "Tissue", "Location", "Lesion", "Response", 
         "PMID")
datatable(Cancer[1:100, ])
```

## Oral toxicity 
```{r, message=FALSE}
Oral_Toxicity <- read_parquet("../../ICE/data/Acute_Oral_Toxicity.parquet") |> 
  select("Chemical Name", "Endpoint", 
         "Response", "Species",
         "PMID")
datatable(Oral_Toxicity[1:100, ])
```

## Endocrine Toxicity 
```{r, message=FALSE}
Endocrine_Toxicity <- read_parquet("../../ICE/data/Endocrine.parquet") |> 
  select("Chemical Name", "Endpoint", 
         "Response", "Receptor Species",
         "Reference", "Reference 2")
datatable(Endocrine_Toxicity[1:100, ])
```

